---
title: "2015 NFL Season Stats"
output: html_document

---

```{r setup, include=FALSE}
#packages ----
library(dplyr)
library(ggplot2)
library(nflscrapR)
library(highcharter)
library(rvest)
library(stringr)

#load 2015 data ----
season <- read.csv("~/R Working Directory/Other/eagles/season.csv")
```

Some ideas for gathering and presenting NFL stats for the upcoming season.  
Code available on githb [here.](https://github.com/brndngrhm/eagles)  
Mainly uses *nflscrapR* package. More details on that [here.](https://github.com/maksimhorowitz/nflscrapR)

# NFL {.tabset}

## Offense {.tabset}

### Passing Attempts
```{r, echo = F, fig.height = 20, fig.width = 10}
#passing attempts
pass.att <- season %>% filter(pass.att > 0) %>% group_by(team,name,team2) %>% summarise(Passing.Attempts = sum(pass.att)) %>% ungroup() %>% arrange(desc(Passing.Attempts))
pass.att$rank <- c(1:nrow(pass.att))

(pass.att.plot <- highchart() %>%
  hc_add_series(name="Passing Attempts", data = subset(pass.att$Passing.Attempts, pass.att$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = pass.att$name, color = pass.att$coloring) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Passing Attempts - Top 40 QBs", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "http://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))

```

### Completions
```{r, echo = F, fig.height=20, fig.width=10}
#completions
#completions
pass.comp <- season %>% filter(pass.comp > 0) %>% group_by(team,name,team2) %>% summarise(Passing.Completion = sum(pass.comp)) %>% ungroup() %>% arrange(desc(Passing.Completion))
pass.comp$rank <- c(1:nrow(pass.comp))

(pass.comp.plot <- highchart() %>%
  hc_add_series(name="Completed Passes", data = subset(pass.att$Passing.Attempts, pass.att$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = pass.att$name, color = pass.att$coloring) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Completed Passes - Top 40 QBs", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```

### Passing Yards
```{r, echo=F, fig.height=20, fig.width=10}
#passing yards
pass.yds <- season %>% filter(passyds > 0) %>% group_by(team,name,team2) %>% summarise(Passing.Yards = sum(passyds)) %>% ungroup() %>% arrange(desc(Passing.Yards))
pass.yds$rank <- c(1:nrow(pass.yds))

(pass.yds.plot <- highchart() %>%
  hc_add_series(name="Passing Yards", data = subset(pass.yds$Passing.Yards, pass.yds$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = pass.yds$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Passing Yards- Top 40 QBs", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```

### Passing TDs
```{r, echo=F, fig.height=20, fig.width=10}
#Passing Touchdowns
pass.tds <- season %>% filter(pass.tds > 0) %>% group_by(team,name,team2) %>% summarise(Passing.tds = sum(pass.tds)) %>% ungroup() %>% arrange(desc(Passing.tds))
pass.tds$rank <- c(1:nrow(pass.tds))

(pass.tds.plot <- highchart() %>%
  hc_add_series(name="Passing Touchdowns", data = subset(pass.tds$Passing.tds, pass.tds$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = pass.tds$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Passing Touchdowns- Top 40 QBs", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```


### Int's Thrown
```{r, echo=F, fig.height=20, fig.width=10}
#Interceptions thrown
pass.int <- season %>% filter(pass.ints > 0) %>% group_by(team,name,team2) %>% summarise(Passing.int = sum(pass.ints)) %>% ungroup() %>% arrange(desc(Passing.int))
pass.int$rank <- c(1:nrow(pass.int))

(pass.int.plot <- highchart() %>%
  hc_add_series(name="Interceptions Thrown", data = subset(pass.int$Passing.int, pass.int$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = pass.int$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Interceptions Thrown - Top 40 QBs", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```


### Rushing Attempts
```{r, echo=F, fig.height=20, fig.width=10}
#Rushing Attempts
rush.att <- season %>% filter(rush.att > 0) %>% group_by(team,name,team2) %>% summarise(rush.att = sum(rush.att)) %>% ungroup() %>% arrange(desc(rush.att))
rush.att$rank <- c(1:nrow(rush.att))

(rush.att.plot <- highchart() %>%
  hc_add_series(name="Rushing Attempts", data = subset(rush.att$rush.att, rush.att$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = rush.att$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Rushing Attempts - Top 40", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```

### Rushing Yards
```{r, echo=F, fig.height=20, fig.width=10}
#Rushing Yards
rush.yds <- season %>% filter(rushyds > 0) %>% group_by(team,name,team2) %>% summarise(rush.yds = sum(rushyds)) %>% ungroup() %>% arrange(desc(rush.yds))
rush.yds$rank <- c(1:nrow(rush.yds))

(rush.yds.plot <- highchart() %>%
  hc_add_series(name="Rushing Yards", data = subset(rush.yds$rush.yds, rush.yds$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = rush.yds$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Rushing Yards - Top 40", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```

### Rushing Yds/Att
```{r, echo=F, fig.height=20, fig.width=10}
#Rushing Yards / Att
rush.yds.att <- season %>% select(rushyds, rush.att, team, name, team2) %>% filter(rush.att > (4*16)) %>% group_by(team,name,team2) %>% summarise(rush.yds.att = (rushyds/rush.att)) %>% ungroup() %>% arrange(desc(rush.yds.att))
rush.yds.att$rank <- c(1:nrow(rush.yds.att))
rush.yds.att$rush.yds.att <- round(rush.yds.att$rush.yds.att, 2)

(rush.yds.att.plot <- highchart() %>%
  hc_add_series(name="Rushing Yards/Attempt", data = subset(rush.yds.att$rush.yds.att, rush.yds$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = rush.yds.att$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Rushing Yards / Attempt - Top 40", align="left") %>%
  hc_subtitle(text="For players with at least 4 carriers per game, 2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))
```

### Rushing TDs
```{r, echo=F, fig.height=20, fig.width=10}
#Rushing TDs
rush.tds <- season %>% filter(rushtds > 0) %>% group_by(team,name,team2) %>% summarise(rush.tds = sum(rushtds)) %>% ungroup() %>% arrange(desc(rush.tds))
rush.tds$rank <- c(1:nrow(rush.tds))

(rush.tds.att.plot <- highchart() %>%
  hc_add_series(name="Rushing Touchdowns", data = subset(rush.tds$rush.tds, rush.tds$rank <=40), type = "bar")  %>%
  hc_xAxis(categories = rush.tds$name) %>%
  hc_chart(zoomType = "x") %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE, borderWidth = 1, shared=T) %>%
  hc_title(text="Rushing Touchdowns - Top 40", align="left") %>%
  hc_subtitle(text="2015 Season (Click & Drag to Zoom)", align="left") %>%
  hc_yAxis(title=" ") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_credits(enabled = TRUE,
             text = "nflscrapR",
             href = "https://github.com/maksimhorowitz/nflscrapR") %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_legend(enabled = FALSE))

```


## Defense {.tabset}

## Special Teams {.tabset}


# Eagles {.tabset}
## Offense {.tabset}
## Defense {.tabset}
## Special Teams {.tabset}